FATE summary results

### 2019-11-22 paper draft.Rmd
Export plankton loadings in table

>>>>

prop1 <- apply(loadings.1, 2, f)
prop1

# export to share with collaborators
q.025 <- function(x) {return(quantile(x, probs=0.025))}
q.975 <- function(x) {return(quantile(x, probs=0.975))}
export <- data.frame(name=names(loadings.1), mean=colMeans(loadings.1), LCI=apply(loadings.1, 2, q.025), UCI=apply(loadings.1, 2, q.975))
export[,2:4] <- round(export[,2:4],3)
export <- export %>%
  arrange(mean)

write.csv(export, "plankton loadings.csv", row.names = F)

keep <- prop1 > 0.95
